---
title: "For Experiment 1 effort ratings"
output: word_document
---

```{r setup, message=FALSE}
library(dplyr)
library(ggplot2)
library(ggbeeswarm)
library(ggpubr)
library(ggsignif)
library(RColorBrewer)
library(lme4)
library(lmeresampler)
library(tidyr)
library(modelr)
library(plotly)
library(equatiomatic)
library(vtable)
library(lmerTest)
library(boot)
library(papaja)
library(broom.mixed)
library(e1071)
library(knitr)
library(kableExtra)
library(patchwork)
library(effectsize)

CurrentSourceWD<-dirname(rstudioapi::getSourceEditorContext()$path)
setwd(CurrentSourceWD)

source('helperRfunctions.R') #homemade functions (for plotting), all in one place

# Function to calculate the mean for bootstrapping
mean_func <- function(data, indices) {
  d <- data[indices]
  return(mean(d))
}
mean_centre_this <- function(x){
  mean_subtracted<- x - mean(x,na.rm=T)
  return(mean_subtracted)
}
TwoWayLineSEsum<-function(din,Xvar,Yvar,GroupVar,
                          Xlabel=Xvar,Ylabel=Yvar,
                          setTitle=" ",
                          setLegendTitle = GroupVar,
                          na_rm_before_print = T,
                          na_omit_on = F,
                          Xrotate = 90,
                          shapeSet = c(16, 1),#default, solid vs hollow circles
                          setAxis = list(),...){
  #general function, like ggline
  #have line between means and error bars over them
  #statistical summary done with mean & SE, not bootstrap CI
  #outputs warning to what rows are not plotted
  #upgraded Jun 2024 to also separate condition GroupVars by shape
  
  if(na_omit_on){
    sumdf <- din %>% 
      group_by(.data[[Xvar]],.data[[GroupVar]],
               .drop = FALSE) %>% #drop = FALSE
      summarize(meanVar = mean(na.omit(.data[[Yvar]])), 
                #seVar = sd(na.omit(.data[[Yvar]])) / sqrt(n()),
                seVar = sd(na.omit(.data[[Yvar]])) / sqrt(sum(!is.na(.data[[Yvar]]))),
                .groups = "drop")
    #n() includes NaN, so should do the same as e.g., nanstd(tac_non(isGPat, :))./sqrt(sum(isGPat))
  }else{
    sumdf <- din %>% 
      group_by(.data[[Xvar]],.data[[GroupVar]]) %>% 
      summarize(meanVar = mean(.data[[Yvar]]), 
                seVar = sd(.data[[Yvar]]) / sqrt(n()),
                .groups = "drop")
    #.groups specified to avoid annoying warning; no grouping left in the sumdf
  }
  
  #clean up sumdf before going into ggplot
  if(na_rm_before_print){
    old_rows<-nrow(sumdf)
    sumdf<-sumdf[!(is.na(sumdf$meanVar) | is.na(sumdf$seVar)),]
    new_rows<-nrow(sumdf)
    n_deleted <- old_rows-new_rows
    if(n_deleted>0){
      warning(sprintf("means and SE of NA removed before plotting; %i rows gone", n_deleted))
    }
  }
  
  #actual plot
  aus<-ggplot(sumdf, 
              aes(x = .data[[Xvar]], y = meanVar, color = .data[[GroupVar]],
                  shape = .data[[GroupVar]])) +
    geom_point() + geom_line(aes(group = .data[[GroupVar]])) +
    geom_errorbar(aes(ymin = meanVar - seVar, ymax = meanVar + seVar), width = 0.02) +
    labs(title = setTitle,
         x = Xlabel, 
         y = Ylabel,
         color = setLegendTitle,shape = setLegendTitle)+
    theme_classic()+
    theme(plot.title = element_text(hjust = 0.5),
          axis.text.x = element_text(angle = Xrotate, vjust = 0.5, hjust=1), #to rotate the x label, which were long
          legend.position = "right")+
    scale_shape_manual(values = shapeSet) 
  
  #add features to plot (axis limits)
  if("y" %in% names(setAxis)){
    aus<-aus+scale_y_continuous(limits = setAxis$y)
  }
  if("x" %in% names(setAxis)){
    aus<-aus+scale_x_discrete(limits = setAxis$x)
  }
  if("colourSet" %in% names(list(...))){
    colourSet <- list(...)$colourSet
    aus<-aus+scale_color_brewer(palette = colourSet)
  }
  
  return(aus)
}
theme_set(theme_classic()+theme(text = element_text(size = 18)))
```


```{r}
load("data_exp1/Exp1megatable_final.RData") #gets mega

#=============================================
#get the pre-registered exclusion
keep<-read.csv('data_exp1/keep_effort_not_failed.csv')
keep<-keep$x

#=============================================
#also: dptp for participant-level information
dptp<-read.csv("data_exp1/Exp1_PtpVarTable_full.csv")
dmod<-read.csv("data_exp1/exp1_BICtable.csv") #for modelling
dptp <-left_join(dptp,dmod,by="prolific_id")
```

```{r}
#=============================================
#IMPORTANT: implement exclusion here
mega$prolific_id<-factor(mega$prolific_id)
mega<-mega[mega$prolific_id %in% keep,]
```

```{r}
# Brief Data Wrangling
mega<-write_up_mega_wrangle(mega,c(0,0,0,0))

mega$noProgress<-1
mega$noProgress[mega$progress_shown]<-0
mega$effort_type<-mega$noProgress
mega$failure<-as.numeric(!mega$isGoalReached)

# there should be NO additional column definitions beyond this point!!!
```


# The Ratings: Subjective experience of effort and progress feedback
```{r}
dNoFail<-mega[mega$isGoalReached,] #exclude where the number of pumps required was not completed

#check if some participants have fewer than six trials in each effort type
sBalanced <-dNoFail %>% group_by(prolific_id,effort_type) %>% 
  summarise(cell_n = n(),.groups = "drop") %>%
  complete(prolific_id, effort_type, fill = list(cell_n = 0)) #grabs those who don't have this condition
keep4ratings <- sBalanced$prolific_id[sBalanced$cell_n >= 6] #no fewer than six trials in each cond

#check if enough cells per participant (enough conditions spanned); exclude the participants
sCheck <- dNoFail %>% group_by(prolific_id,actual_offer,effort_type) %>% 
  summarise(cell_n = n()) #count the number of data points in each cell
sCheck <- sCheck[sCheck$cell_n>3,]
s1<-as.data.frame(table(sCheck$prolific_id[sCheck$effort_type==1]))
s2<-as.data.frame(table(sCheck$prolific_id[sCheck$effort_type==0]))

#now exclude those with no more than two cells fitting the criteria
enoughNoProgress<-s1$Var1[s1$Freq>1]
enoughWithProgress<-s2$Var1[s2$Freq>1]

keep4ratings <- intersect(keep4ratings,intersect(enoughNoProgress,enoughWithProgress))

dlme<-dNoFail[dNoFail$prolific_id %in% keep4ratings,]
```

```{r}
#wrangle data so avoid those factors
dlme$noProgress<-1
dlme$noProgress[dlme$progress_shown]<-0
dlme$effort_type<-dlme$noProgress
dlme$failure<-as.numeric(!dlme$isGoalReached)

m1.0<-lmer(rating~effort_level*effort_type+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id), dlme)
m1.1<-lmer(rating~effort_level*effort_type+(1|prolific_id)+(0+effort_level|prolific_id),dlme)
m1.2<-lmer(rating~effort_level*effort_type+(1|prolific_id)+(0+effort_type|prolific_id),dlme)
m2<-lmer(rating~effort_level+effort_type+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id),dlme)
m3<-lmer(rating~effort_level+effort_type+(1|prolific_id)+(0+effort_level|prolific_id),dlme)
m4<-lmer(rating~effort_level+effort_type+(1|prolific_id)+(0+effort_type|prolific_id),dlme)
m5<-lmer(rating~effort_level+effort_type+(1|prolific_id),dlme)
m6<-lmer(rating~effort_level*effort_type+(1|prolific_id),dlme)

tBIC<-BIC(m1.0,m1.1,m1.2,m2,m3,m4,m5,m6)
tBIC$diffBIC<-tBIC$BIC-min(tBIC$BIC)
tBIC
apa_table(tBIC)
```


Set winner and do model checks
```{r}
m1<-m3
apa_table(apa_print(m1)$table)
```

Further wrangle to get exact p values?
```{r}
m1pVal<-summary(m1)
m1pVal$coefficients
```

```{r}
performance::check_model(m1,
                         check=c("linearity","homogeneity","qq","outliers"))
```

Visualise: effort rating plots
```{r}
d4p<-dlme #define the data frame for plotting
d4p<-d4p %>% 
  group_by(prolific_id) %>% 
  mutate(rating = mean_centre_this(rating))
sumRatings<-d4p[d4p$progress_shown,] %>% 
  group_by(prolific_id,effort_level) %>% 
  summarize(MeanRating = mean(rating), SE = sd(rating) / sqrt(n()))
#repeat for no progress
sumRatings2<-d4p[!d4p$progress_shown,] %>% 
  group_by(prolific_id,effort_level) %>% 
  summarize(MeanRating = mean(rating), SE = sd(rating) / sqrt(n()))

ggarrange(
ggplot(sumRatings, aes(x = effort_level+0.3, y = MeanRating,color = prolific_id)) +
  geom_point(alpha=0.1) + geom_line(aes(group = prolific_id),alpha=0.1) +
  stat_summary(aes(group=1),
               fun.data = mean_cl_boot,
               size = 0.2,
               position=position_nudge(x = 0.01, y = 0))+
  labs(title = "PF+", 
       x = "Effort Level", 
       y = "Rating \n (mean-centred)")+
  scale_x_continuous(limits = c(0.3,0.75)+0.3)+
  scale_y_continuous(limits = c(-0.40,0.55))+
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "none")+theme(text=element_text(size=14)),

ggplot(sumRatings2, aes(x = effort_level+0.3, y = MeanRating,color = prolific_id)) +
  geom_point(alpha=0.1) + geom_line(aes(group = prolific_id),alpha=0.1) +
  stat_summary(aes(group=1),
               fun.data = mean_cl_boot,
               size = 0.2,
               position=position_nudge(x = 0.01, y = 0))+
  labs(title = "PF-", 
       x = "Effort Level", 
       y = "Rating \n (mean-centred)")+
  scale_x_continuous(limits = c(0.15,0.75)+0.3)+
  scale_y_continuous(limits = c(-0.40,0.55))+
  theme(plot.title = element_text(hjust = 0.5),axis.title.y = element_blank(),
        legend.position = "none")+theme(text=element_text(size=14)),
nrow=1
)
ggsave('figs/ratings_exp1_supplementary.jpg',width=8.4,height=4.51)
```


# Include all trials + analyse Fail on effort ratings
```{r}
f1m1 <- lmer(rating~effort_level*effort_type*failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f1m2 <- lmer(rating~effort_level*effort_type*failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id), mega)
f1m3 <- lmer(rating~effort_level*effort_type*failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+failure|prolific_id), mega)
f1m4 <- lmer(rating~effort_level*effort_type*failure+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f1m5 <- lmer(rating~effort_level*effort_type*failure+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f1m6 <- lmer(rating~effort_level*effort_type*failure+(1|prolific_id)+(0+effort_level|prolific_id), mega)
f1m7 <- lmer(rating~effort_level*effort_type*failure+(1|prolific_id)+(0+effort_type|prolific_id), mega)
f1m8 <- lmer(rating~effort_level*effort_type*failure+(1|prolific_id)+(0+failure|prolific_id), mega)
f1m9 <- lmer(rating~effort_level*effort_type*failure+(1|prolific_id), mega)

f2m1 <- lmer(rating~effort_level*effort_type+failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f2m2 <- lmer(rating~effort_level*effort_type+failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id), mega)
f2m3 <- lmer(rating~effort_level*effort_type+failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+failure|prolific_id), mega)
f2m4 <- lmer(rating~effort_level*effort_type+failure+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f2m5 <- lmer(rating~effort_level*effort_type+failure+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f2m6 <- lmer(rating~effort_level*effort_type+failure+(1|prolific_id)+(0+effort_level|prolific_id), mega)
f2m7 <- lmer(rating~effort_level*effort_type+failure+(1|prolific_id)+(0+effort_type|prolific_id), mega)
f2m8 <- lmer(rating~effort_level*effort_type+failure+(1|prolific_id)+(0+failure|prolific_id), mega)
f2m9 <- lmer(rating~effort_level*effort_type+failure+(1|prolific_id), mega)

f3m1 <- lmer(rating~effort_level+effort_type+failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f3m2 <- lmer(rating~effort_level+effort_type+failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id), mega)
f3m3 <- lmer(rating~effort_level+effort_type+failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+failure|prolific_id), mega)
f3m4 <- lmer(rating~effort_level+effort_type+failure+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f3m5 <- lmer(rating~effort_level+effort_type+failure+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f3m6 <- lmer(rating~effort_level+effort_type+failure+(1|prolific_id)+(0+effort_level|prolific_id), mega)
f3m7 <- lmer(rating~effort_level+effort_type+failure+(1|prolific_id)+(0+effort_type|prolific_id), mega)
f3m8 <- lmer(rating~effort_level+effort_type+failure+(1|prolific_id)+(0+failure|prolific_id), mega)
f3m9 <- lmer(rating~effort_level+effort_type+failure+(1|prolific_id), mega)

f4m1 <- lmer(rating~effort_level*failure+effort_type+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f4m2 <- lmer(rating~effort_level*failure+effort_type+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id), mega)
f4m3 <- lmer(rating~effort_level*failure+effort_type+(1|prolific_id)+(0+effort_level|prolific_id)+(0+failure|prolific_id), mega)
f4m4 <- lmer(rating~effort_level*failure+effort_type+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f4m5 <- lmer(rating~effort_level*failure+effort_type+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f4m6 <- lmer(rating~effort_level*failure+effort_type+(1|prolific_id)+(0+effort_level|prolific_id), mega)
f4m7 <- lmer(rating~effort_level*failure+effort_type+(1|prolific_id)+(0+effort_type|prolific_id), mega)
f4m8 <- lmer(rating~effort_level*failure+effort_type+(1|prolific_id)+(0+failure|prolific_id), mega)
f4m9 <- lmer(rating~effort_level*failure+effort_type+(1|prolific_id), mega)

f5m1 <- lmer(rating~effort_level+effort_type*failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f5m2 <- lmer(rating~effort_level+effort_type*failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+effort_type|prolific_id), mega)
f5m3 <- lmer(rating~effort_level+effort_type*failure+(1|prolific_id)+(0+effort_level|prolific_id)+(0+failure|prolific_id), mega)
f5m4 <- lmer(rating~effort_level+effort_type*failure+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f5m5 <- lmer(rating~effort_level+effort_type*failure+(1|prolific_id)+(0+effort_type|prolific_id)+(0+failure|prolific_id), mega)
f5m6 <- lmer(rating~effort_level+effort_type*failure+(1|prolific_id)+(0+effort_level|prolific_id), mega)
f5m7 <- lmer(rating~effort_level+effort_type*failure+(1|prolific_id)+(0+effort_type|prolific_id), mega)
f5m8 <- lmer(rating~effort_level+effort_type*failure+(1|prolific_id)+(0+failure|prolific_id), mega)
f5m9 <- lmer(rating~effort_level+effort_type*failure+(1|prolific_id), mega)
```

```{r}
bigBIC<-BIC(f1m1,f1m2,f1m3,f1m4,f1m5,f1m6,f1m7,f1m8,f1m9,
            f2m1,f2m2,f2m3,f2m4,f2m5,f2m6,f2m7,f2m8,f2m9,
            f3m1,f3m2,f3m3,f3m4,f3m5,f3m6,f3m7,f3m8,f3m9,
            f4m1,f4m2,f4m3,f4m4,f4m5,f4m6,f4m7,f4m8,f4m9,
            f5m1,f5m2,f5m3,f5m4,f5m5,f5m6,f5m7,f5m8,f5m9)
bigBIC$diffBIC<-bigBIC$BIC-min(bigBIC$BIC)
bigBIC
```

New winner: f3m3, rating~effort_level+effort_type+failure, with random slopes for effort level and failures but NOT effort type.

The effect of effort type for this sensitivity analysis: `r apa_print(f3m3)$full_result$effort_type`...

Now the table:
```{r}
#summary(f3m1)
apa_table(apa_print(f3m3)$table)
```